### 2014-08-14 doc/thesis/typedlua.tex
Forgot to mention privacy rules and multiple inheritance in the OO section

%Besides interfaces, Typed Lua will also introduce classes.
%We want to offer classes as a standard way for writing code that
%Lua programmers are already using, but without tying them to a
%specific model.
%Our classes will not include static attributes and will also not offer
%privacy rules.

@@

The current version of Typed Lua has some limitations regarding
the use of \texttt{setmetatable}.
One limitation is that Typed Lua does not have polymorphism,
so programmers cannot hide the calls to \texttt{setmetatable} behind
nicer abstractions, as some Lua libraries do.
Another limitation is that Typed Lua does not support operator overloading,
so programmers cannot use \texttt{setmetatable} to change the behavior
of predefined operations, as some Lua libraries do.

>>>>

@@

The current version of Typed Lua has some limitations regarding
the use of \texttt{setmetatable} that are on plans for future work.
One limitation is that Typed Lua does not have polymorphism,
so programmers cannot hide the calls to \texttt{setmetatable} behind
nicer abstractions, as some Lua libraries do.
Another limitation is that Typed Lua does not support operator overloading,
so programmers cannot use \texttt{setmetatable} to change the behavior
of predefined operations, as some Lua libraries do.

Our classes system also does not support multiple inheritance
and does not offer privacy rules, but these limitations are not
on plans for future work anyway.
